%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
% \input{glyphtounicode}  % Commented out - file not found


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{8pt}
\setlength{\footskip}{8pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.50in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Slightly tighter lines to help keep the resume to one page
\linespread{0.96}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\[-2pt]
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabularx}{\textwidth}{@{}Xr@{}}
      \small#1 & \textbf{\small #2}\\
    \end{tabularx}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, topsep=2pt, itemsep=1pt, parsep=0pt, partopsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-1pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{kasturipranavi21@gmail.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-306-640-7063 \\
% \end{tabular*}

\vspace{-16pt}
\begin{center}
    {\Huge \scshape Sai Pranavi Kasturi} \\ 
    
    \small +1-437-388-2829 | \underline{pkasturi@uwaterloo.ca} | \href{https://linkedin.com/in/sai-pranavi-kasturi-704807298}{\underline{linkedin.com/in/sai-pranavi-kasturi-704807298}} | \href{https://github.com/ispilledmymilk}{\underline{github.com/ispilledmymilk}}
\end{center}

\vspace{-2pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Sept 2024 -- Present}
      {Bachelors of Computer Science - 2B}{Waterloo, Canada}
      
      % {Programming Principles(71), Linear Algebra(87), Calculus(84), Software Engineering(83), Algebra Honors(80)\small}
  \resumeSubHeadingListEnd
  

\section{Technical Skills}
\begin{itemize}[leftmargin=0.05in, label={}]
  \small\item{
    Python (Pandas, NumPy, Matplotlib, SciPy, PyTorch), Java, C++, GoLang, JavaScript/TypeScript, Spring Boot, Angular, REST APIs, JWT, PostgreSQL, MongoDB, SQL, Git, Docker, CI/CD, DevOps, Linux, Bash, Shell Scripting, AWS, Azure, Maven, JUnit, Flyway, Karma, GTest, Postman, Supabase, Playwright, Raspberry Pi, Agile, JIRA, Excel, Figma, Tableau, Power BI, DocketQA
  }
\end{itemize}
 \vspace{-4pt}

%-----------EXPERIENCE-----------

\section{Experience}

    \resumeSubHeadingListStart
     \vspace{-2pt} 
    \resumeSubheading
        {Automation Developer $|$ Zoocasa $|$ Toronto, Canada}{Jan 2026 - Apr 2026} 
      {}{} 
          \resumeItemListStart
            \resumeItem{Built end-to-end\textbf{ automation infrastructure} using Playwright and Postman across JS and GoLang codebases, reducing manual testing overhead by \textbf{60\%} and \textbf{accelerating release cycles} across all active product teams\textbf{(Frontend and Backend teams)}}
            \resumeItem{Engineered an \textbf{AI-powered} feed compliance bot that answers natural language regulatory queries, \textbf{auto-generates} structured \textbf{JSON configs} from documents, and triggers \textbf{real-time workflow updates} on document changes, eliminating manual tracking.}
            \vspace{-4pt}
            \resumeItem{Conducted \textbf{root cause analysis} on production failures by reviewing \textbf{cross-language codebases} to identify \textbf{systemic failure patterns}, reducing \textbf{defect recurrence} in high-risk areas and improving overall \textbf{system reliability} by \textbf{47\%}.}
            \resumeItem{Contributed to full \textbf{SDLC} including \textbf{sprint planning}, effort estimation, and feature prioritization in an \textbf{Agile environment}, collaborating \textbf{cross-functionally} with developers, designers, and product managers to \textbf{meet delivery timelines}.}
          \resumeItemListEnd
          \vspace{-1pt} 
      \resumeSubheading
        {QA Specialist $|$ DocTalk $|$ Toronto, Canada}{May 2025 - Aug 2025}
      {}{}   
          \resumeItemListStart
            \resumeItem{Architected scalable automated testing infrastructure covering \textbf{1000+} test scenarios across \textbf{REST APIs} and frontend services using \textbf{Playwright} and \textbf{Postman}, improving defect detection rates and reducing regression risk prior to each production release.} 
            \resumeItem{Owned frontend development and maintenance of a \textbf{B2B SaaS} platform, independently implementing new user-facing features, resolving \textbf{UI bugs}, and improving \textbf{UX workflows} to \textbf{enhance usability} for clinical and administrative end users.}   
            \resumeItem{Defined and documented \textbf{1500+} \textbf{functional requirements} and test cases covering \textbf{edge cases and failure scenarios}, bridging engineering and product teams to align technical execution with business goals and ensure on-time, high-quality feature delivery.}
          \resumeItemListEnd
          \vspace{-1pt}
    \resumeSubheading
        {Market Analyst Consultant $|$ Happy Sneeze $|$ USA, Remote}{Apr 2024 - Jul 2024}
        {}{}   
          \resumeItemListStart
            \resumeItem{Developed a competitive landscape map by conducting extensive data analysis and financial performance assessments of \textbf{15+} key players in the health market, leveraging \textbf{ETL techniques }to extract and process large volumes of data into actionable insights.}
            \vspace{-4pt}        
            \resumeItem{Performed comprehensive research using \textbf{data transformation} and \textbf{reporting} techniques to analyze annual growth rate, key segments, and emerging trends, delivering structured reports that directly informed executive-level \textbf{strategic decisions}.}        
            \resumeItem{Identified \textbf{10} valuable partners and developed a targeted \textbf{outreach strategy} with personalized messaging frameworks to engage stakeholders in discussions, ensuring alignment with corporate growth goals, market positioning and partnership objectives}.        
          \resumeItemListEnd
          \vspace{-1pt}

    \resumeSubheading
        {IT Support Help $|$ Indian Language School $|$ Lagos, Nigeria}{Apr 2022 - Mar 2023}
      {}{}
          \resumeItemListStart
            \resumeItem{Provided technical support to \textbf{1500+} students, resolving \textbf{90} issues weekly related to hardware, software, and network.}
            \resumeItem{Managed tickets and troubleshot \textbf{50+} requests per week, including system errors, printer malfunctions, and access issues.}
            \resumeItem{Assisted in maintaining \textbf{200+} campus devices, performing updates, installations, and security patches to ensure uptime.}
          \resumeItemListEnd
                
   \resumeSubHeadingListEnd 

%-----------PROJECTS-----------
\vspace{-4pt}
\section{Projects}
    \resumeSubHeadingListStart

    \resumeProjectHeading
          {\textbf{OmenAI} \textbar\ \textbf{TD Best AI hack to detect financial fraud} $|$ \emph{\textbf{Python(scikit-learn), PostgreSQL, NextJS, Redis}}}{Mar 2026}
    \resumeItemListStart
    \resumeItem{Built a \textbf{real-time} \textbf{surveillance dashboard} detecting insider trading on prediction markets using a \textbf{multi-phase pipeline} combining rule-based scoring, \textbf{Isolation Forest} \textbf{anomaly detection}, and \textbf{AI-analyzed risk explanations}.}
    \resumeItem{Engineered an \textbf{end-to-end fraud detection} system that ingested and scored \textbf{600K+ live trades} across wallet signals like win rate, bet sizing, and trade velocity to classify risk tiers across market categories.}
            % \resumeItem{\textit{Streamlined data processing}, enhancing the accuracy and efficiency of the system, while leveraging \textit{version control strategies} through GitLab for seamless project collaboration}
            \resumeItem{Delivered a \textbf{live dashboard }with streaming trade feeds, \textbf{Blockchain information}, radar \textbf{visualizations}, and \textbf{wallet deep-dives} with no labeled ground-truth dataset.}
          \resumeItemListEnd 

      \resumeProjectHeading
          {\textbf{Weathwise} $|$ \emph{\textbf{Java, Spring Boot, Angular, TypeScript, PostgreSQL, MongoDB, Docker, JWT, Postman}}}{Dec 2025}
          \resumeItemListStart
            \resumeItem{Designed a \textbf{stateless, }\textbf{JSON Web Token-authenticated API} with \textbf{per-user isolation} on all financial reads/writes, schema versioning for relational data, and \textbf{environment-driven configuration} suitable for \textbf{containerized deploys}.}
            \resumeItem{Implemented a \textbf{multi database architecture} that separated \textbf{transactional and analytical workloads} across relational and document stores. Built resilient \textbf{per user batch processing} to \textbf{isolate failures} and keep the full job running.}
            \resumeItem{Delivered \textbf{production ready }infrastructure with \textbf{Docker Compose}, database readiness checks, and a \textbf{reverse proxied SPA deployment}, and contract driven \textbf{API documentation }and \textbf{automated tests} for \textbf{authentication and aggregation workflows}.}
          \resumeItemListEnd
          \resumeProjectHeading
{\textbf{eXplicit} $|$ 
\emph{\textbf{Python, Google Drive API, OpenAI, JSON, 
Workflow Automation}}}{Jan 2026}
\resumeItemListStart
    \resumeItem{Built an \textbf{AI-powered compliance assistant} that answers 
    \textbf{natural language} questions about real estate feed regulations, 
    reducing time spent manually reviewing compliance documentation.}
    \resumeItem{Engineered an \textbf{automated pipeline} that parses regulatory 
    documents from Google Drive and generates \textbf{structured} \textbf{JSON }
    \textbf{configuration files}, \textbf{eliminating manual data entry}.}
    \resumeItem{Implemented \textbf{event-driven workflow automation} that 
    triggers \textbf{JSON regeneration} on document updates in Google Drive, 
    ensuring compliance data is always in sync with the latest 
    regulatory changes.}
\resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Smart Mirror- AuraGlass} $|$ \emph{\textbf{Bash, Javascript, GitLab, Open AI, API, Raspberry Pi4}}}{Oct 2024}
          \resumeItemListStart
            \resumeItem{Created a smart mirror with \textbf{7} modules including Google, Spotify and Claude. Oversaw team operations throughout the SDLC.}
            \resumeItem{Demonstrated the ability to conduct research or applied Computer Science projects with an accuracy of \textbf{90 per cent}.}
            \resumeItem{Worked on the implementation, the customization and the debugging of modules for a smooth running of the mirror.}
          \resumeItemListEnd
          \vspace{-1pt}
          
          \resumeProjectHeading
          {\textbf{Running Alarm Clock - Alarmy} $|$ \emph{\textbf{Java, Arduino, Git}}}{Sept 2023}
          \resumeItemListStart
            \resumeItem{Developed and implemented a comprehensive test environment for the Arduino-based runaway alarm clock, using unit and integration testing. Used GitHub for version control, bug tracking, and code refactoring to achieve \textbf{\(80 \%\)} accuracy.}
            \resumeItem{Created \textbf{20+} test cases to validate functionality, edge cases, and failure modes. Utilized Arduino IDE for automated testing and debugging, ensuring system stability and performance.}
            \resumeItem{Documented \textbf{15+} test cases with inputs, expected outputs, and actual results for regression and performance validation.
}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-2pt}
%-----------EXPERIENCE-----------
\section{Extracurriculars}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Events Director $|$ UW Product Management Club $|$ Waterloo, Canada}{Sept 2025 - Dec 2025}
      {}{}
      \resumeItemListStart
        \resumeItem{Lead E2E \textbf{event planning and execution} for campus organization events, managing logistics from ideation to follow-up.}
        \resumeItem{Coordinate \textbf{promotional campaigns} with the marketing team to increase event attendance and engagement.}
        \resumeItem{Organize teams, delegate tasks effectively, and lead setup and teardown for small- and large-scale events.}
      \resumeItemListEnd
      \vspace{-3pt}
    \resumeSubheading
      {Campus Ambassador $|$ Velocity $|$ Waterloo, Canada}{Sept 2025 - Dec 2025}
      {}{}
      \resumeItemListStart
        \resumeItem{Managed event-day operations, including check-in, food stations, supply distribution, wayfinding, and attendee support.}
        \resumeItem{Promoted campus events and programs through \textbf{social media campaigns} and word-of-mouth outreach.}
        \resumeItem{Organized social activities to engage the Velocity community and strengthen campus connections.}
      \resumeItemListEnd
      \vspace{-3pt}
    \resumeSubheading
      {Engineering and Campus Ambassador $|$ University of Waterloo $|$ Waterloo, Canada}{Sept 2024 - Present}
      {}{}
      \resumeItemListStart
        \resumeItem{Represented campus programs and helped attract prospective students to engineering and campus housing.}
        \resumeItem{Guided \textbf{50+} students during tours, answering questions about engineering life, schedules, and housing.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-4pt}
\section{Certifications and Awards}
%\vspace{-2pt}
    \resumeSubHeadingListStart
      \item[]
          \resumeItemListStart
          %\vspace{-2pt}
            \resumeItem{Completed \textbf{AWS Beginners certification} and \textbf{Data Analysis Certification by Linkedin, API Postman Certification}}
            \resumeItem{Won \textbf{Gold Sponsor TD Best AI Hack to detect financial fraud} at \textbf{GenAI Genesis hackathon 2026}}
           % \vspace{-2pt}
          
            
          \resumeItemListEnd
          \vspace{-1pt}
        
   \resumeSubHeadingListEnd
%-----------EDUCATION-----------


\end{document}